Correlations between gender and research topics at three major archaeology conferences

### 2020-10-29 analysis/paper/paper.Rmd
add some discussion
edits to para about Sinclair

In an article by @sinclair2016intellectual, he has compared the relative standings between men and women researchers in terms of number of citations made by other authors in the field of archaeology. Among the list of 50 most cited authors, only 6 of them (12%) are women, meaning that recognition in terms of citation are still mostly given to men, similar theme can be seen even if we increase to top 250 authors, with 19% being women [@sinclair2016intellectual]. After analyzing the most cited authors and their articles' thematic clusterings, it can be seen that there is relatively more women authors whose article is in the category of Archaeology of Early State Societies in the Americas (N and C America) with 46% women authors,the category of Archaeological chemistry (esp. lipids analysis) with 40% women authors, Isotope analysis with 30% women authors, and dating (esp. thermoluminescence and magnetics) with 30% women authors, while the average women author that are cited in the field of archaeology as a whole is around 14%. One possible reason could be that men and women simply have preferences over different topics and this is one reason why we want to examine if there's some correlation between gender and topics of presentation.

@@

>>>>

@sinclair2016intellectual, compared the relative standings between men and women researchers in terms of number of citations made by other authors in the field of archaeology. Among the list of 50 most cited authors, only 6 of them (12%) are women, meaning that recognition by citation is still mostly given to men. A similar result can be seen if we increase the sample to the top 250 authors, with 19% women [@sinclair2016intellectual]. After analyzing the most cited authors and their articles' thematic clusterings, we see that there are relatively more women authors in the category of Archaeology of Early State Societies in the Americas (N and C America) with 46% women authors. Other categories with high proportions of women are Archaeological chemistry (esp. lipids analysis) with 40% women authors, Isotope analysis with 30% women authors, and dating (esp. thermoluminescence and magnetics) with 30% women authors. The average women author cited in the field of archaeology as a whole is around 14%. Sinclair concludes that the higher representation of women as cited authors on topics of laboratory analysis supports Gero's claim that women in archaeology were most active in laboratory-based activities rather than excavation/fieldwork related activities.

@@

Talk about Thelwall... say that these gender differences exist, but
